\cvsection{Presentations}

\begin{cventries}

  \cventry
  {Parti, G. \& Joo I. (2024). \textit{Crowd of Cardamoms: The Etymological Origins of Cardamom in Chinese}} % Role
  {Language of Food conference, Nanyang Technological University \href{https://www.ntu.edu.sg/soh/news-events/events/detail/2024/01/29/research-events/the-language-of-food-exploring-culinary-communication-and-culture}{\faExternalLink}} % Event
  {Singapore} % Location
  {Jan. 2024} % Date(s)
  {
    %   \begin{cvitems} % Description(s)
    %     \item {Introduced basic procedure for penetration testing and how to use Metasploit}
    %   \end{cvitems}
  }

  

  \cventry
  {Parti, G. (2023). \textit{A fűszerek nyelvének feltérképezése: korpusz alapú, filológiai tanulmány a fűszerek világáról [Mapping the Language of Spices A Corpus-Based, Philological Study on the Words of the Spice Domain]}} % Role
  {Csoma de Kőrös Society, 2023 Talks \href{https://www.youtube.com/watch?v=udy1Hrn0wc0}{\faExternalLink}} % Event
  {Budapest/Online} % Location
  {Apr. 2023} % Date(s)
  {
    %   \begin{cvitems} % Description(s)
    %     \item {Introduced basic procedure for penetration testing and how to use Metasploit}
    %   \end{cvitems}
  }

  \cventry
    {Parti, G., \& Huang, C.-R. (2022). \textit{The Naming Principles of Novel Cultural Items: A Perspective from the Spice Domain.}} % Role
    {The 31st Joint Workshop on Linguistics and Language Processing \href{https://jwllp31.github.io/program/}{\faExternalLink}} % Event
    {Seoul/Online} % Location
    {Dec. 2022} % Date(s)
    {
    %   \begin{cvitems} % Description(s)
    %     \item {Introduced basic procedure for penetration testing and how to use Metasploit}
    %   \end{cvitems}
    }


  \cventry
    {Parti, G., \& Huang, C.-R. (2022). \textit{Fragrance from the periphery and beyond: Mapping the origins of foreign spices in Chinese materia medica.} (Poster)} % Role
    {Botanical Symposium 2022: Exploring Innovative Approaches in Chinese Medicines \href{https://event.fourwaves.com/botanicalsymposium2022/abstracts/1ea06222-f8a6-400c-8c92-de4e419a56f3}{\faExternalLink}} % Event % -- From Bench to Bedside
    {Hong Kong/Online} % Location
    {Dec. 2022} % Date(s)
    {
    %   \begin{cvitems} % Description(s)
    %     \item {Introduced basic procedure for penetration testing and how to use Metasploit}
    %   \end{cvitems}
    }

\end{cventries}
