\cvsection{Publications} %Using template of 'committees'

\textsc{Journal articles}

\begin{cvhonors}

  \cvhonor
  {Parti, G.} % Position
  {Mapping the Language of Spices A Corpus-Based, Philological Study on the Words of the Spice Domain. \textit{Sino-Platonic Papers, 338}. \url{https://www.sino-platonic.org/}} % Committee
  {Online} % Location
  {2024} % Date(s)

\end{cvhonors}

\textsc{Conference papers}

\begin{cvhonors}

\cvhonor
{Luo, X., Gábor, P., \& Huang, C.-R.} % Position
{\textit{Gender Variation in Mix-Gender Conversations in the Semi-institutional Discourse: The Case of Talk Show.} In Chinese Lexical Semantics 24th Workshop, CLSW 2023
Singapore, Singapore, May 19–21, 2023 Revised Selected Papers, Part II, 274-285. \url{https://link.springer.com/chapter/10.1007/978-981-97-0586-3_22}} % Committee
{Singapore} % Location
{2023} % Date(s)

\cvhonor
{Parti, G., Liesenfeld, A., \& Huang, C.-R.} % Position
{\textit{Animosity and Suffering: Metaphors of BITTERNESS in English and Chinese.} Proceedings of the 35th Pacific Asia Conference on Language, Information and Computation, 700–710. \url{https://aclanthology.org/2021.paclic-1.74}} % Committee
{Shanghai/Online} % Location
{2021} % Date(s)

\cvhonor
{Liesenfeld, A., Parti, G., \& Huang, C.-R.} % Position
{\textit{Deep Learning Meets Private Talk: Conversational AI Can Predict Speaker Traits by Eavesdropping for Only 30 Seconds.} Mensch Und Computer 2021, 547–551. \url{https://doi.org/10.1145/3473856.3474012}} % Committee
{IngolstadtOnline} % Location
{2021} % Date(s)

\cvhonor
{Liesenfeld, A., Parti, G., \& Huang, C.-R.} % Position
{\textit{Scikit-Talk: A Toolkit for Processing Real-world Conversational Speech Data.} Proceedings of the 22nd Annual Meeting of the Special Interest Group on Discourse and Dialogue, 252–256. \url{https://aclanthology.org/2021.sigdial-1.26}} % Committee
{Singapore/Online} % Location
{2021} % Date(s)

\cvhonor
{Liesenfeld, A., Parti, G., Hsu, Y.-Y., \& Huang, C.-R.} % Position
{\textit{Predicting Gender and Age Categories in English Conversations Using Lexical, Non-Lexical, and Turn-Taking Features.} Proceedings of the 34th Pacific Asia Conference on Language, Information and Computation, 157–166. \url{https://aclanthology.org/2020.paclic-1.19}} % Committee
{Hanoi/Online} % Location
{2020} % Date(s)

\end{cvhonors}

\textsc{Theses}

\begin{cvhonors}

\cvhonor
{Parti, G.} % Position
{\textit{Mapping the Language of Spices A Corpus-Based, Philological Study on the Words of the Spice Domain.} [Ph.D. thesis]. The Hong Kong Polytechnic University. \url{https://theses.lib.polyu.edu.hk/handle/200/12389}} % Committee
{Hong Kong} % Location
{2023} % Date(s)

\cvhonor
{Parti, G.} % Position
{\textit{
Arab-indiai kapcsolatok a középkorban: Az indiai-óceáni tengeri kereskedelem [Arab-India Relations in the Middle Ages: The Indian Ocean Maritime Trade].} [M.A. thesis]. Eötvös Loránd University. \url{}} % Committee
{Budapest} % Location
{2017} % Date(s)

\cvhonor
{Parti, G.} % Position
{\textit{
  A szebíl-kuttáb Kairóban [The Sabil-Kuttab in Cairo].} [B.A. thesis]. Eötvös Loránd University. \url{}} % Committee
{Budapest} % Location
{2014} % Date(s)

\cvhonor
{Parti, G.} % Position
{\textit{
Középkori muszlim utazók és geográfusok a Koreai-félszigetről [Medieval Muslim Travelers and Geographers on the Korean Peninsula].} [B.A. thesis]. Eötvös Loránd University. \url{}} % Committee
{Budapest} % Location
{2013} % Date(s)

\end{cvhonors}

